---
title: "case_study"
author: "Joe LaRocca"
date: "2024-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(leaflet)
```

```{r}
library(p8105.datasets)

data(nyc_airbnb)
```

```{r}

view(nyc_airbnb)

```

## Brainstorming Questions

* Where are the maximum and minimum prices? What's the average price?
* Where are prices going up and down over time?
* What's the relationship between number of reviews and average reviews?
* Does room type affect availability?
* What's the location of the unit? What areas are popular?
  * Does popularity correlate with number of units? Average price?
* Are there repeat hosts?
  * If so, what does that mean?
  
#### Find mean, max, min, price  

```{r}

mean_price = nyc_airbnb %>%
  pull(price) %>%
  mean()

max_price = nyc_airbnb %>%
  pull(price) %>%
  max()

min_price = nyc_airbnb %>%
  pull(price) %>%
  min()

c(min_price, mean_price, max_price)

```

#### Finding mean price by room type

```{r}

nyc_airbnb %>%
  group_by(room_type) %>%
  summarize(mean_price = mean(price))

```

#### Compare price across boroughs using a visual

```{r}

nyc_airbnb %>%
  ggplot(aes(x = price, fill = neighbourhood_group)) +
  geom_histogram() + 
  facet_grid(. ~ neighbourhood_group) +   
  scale_x_continuous(limits = c(0, 250))

```

#### Side-by-side boxplots of price by borough -- log transformed!

```{r}

nyc_airbnb %>%
  ggplot(aes(x = neighbourhood_group, y = log(price))) +
  geom_boxplot()

```

#### Numeric Summary of Prices by Manhattan Neighborhood

```{r}

nyc_airbnb %>%
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000,
    room_type == "Entire home/apt") %>%
  group_by(neighbourhood) %>%
  summarize(mean_price = mean(price)) %>%
  arrange(mean_price)

```

#### Plot Latitude Vs. Longitude for Manhattan

```{r}

nyc_airbnb %>%
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000) %>%
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point()

```

#### Violin Plots of Price by Manhattan Neighborhood

```{r}

nyc_airbnb %>%
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000,
    room_type == "Entire home/apt") %>%
  mutate(neighbourhood = as.factor(neighbourhood)) %>%
  ggplot(aes(x = neighbourhood, y = price)) + 
  geom_violin() +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))

```

#### Experimenting With Leaflet to Make a Map

```{r}

pal = colorNumeric(
  palette = "viridis",
  domain = nyc_airbnb$review_scores_location)

nyc_airbnb %>%
  filter(
    neighbourhood_group == "Manhattan",
    price < 1000
  ) %>%
  leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(
    ~lat, ~long, 
    color = ~ pal(review_scores_location), radius = 0.2
  )

```

